Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Weight and Convex Input Constraints

### 2025-04-17 manuscript.tex
add forth controlller

% ------------------------------------
% Comparative Study
% ------------------------------------
For a comparative study, we implemented 3 controllers.
The properties of the controllers are summarized in Table~\ref{table:controllers}.

@@

@@

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers used in simulation}
    \label{table:controller}
    \centering
    \begin{tabular}{c l l}
    \hline
        \!&\!\bf{Description}\!&\!\bf{Input Constraint}\!\\
    \hline
    \hline
        (C$_1$) & proposed & $\overline{\tau}=10$ and $\overline{\tau}_2=-\underline{\tau}_2=2.5$ \\
    \hline
        (C$_2$) & aux. sys. & $\overline{\tau}_1=-\underline{\tau}_1=9.682$ and $\overline{\tau_2}=-\underline{\tau_2}=2.5$ \\
    \hline
        (C$_3$) & small $\beta_i$ & $\overline{\tau}=10$ and $\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
    \hline
    \end{tabular}
    \label{table:controllers}
\end{table}

@@

% ------------------------------------
% Norm of error in Episode 1: 
% C1 r1 ep1: 0.389
% C1 r2 ep1: 0.426
% C2 r1 ep1: 0.403
% C2 r2 ep1: 0.456
% C3 r1 ep1: 0.370
% C3 r2 ep1: 0.427
% Norm of error in Episode 2: 
% C1 r1 ep2: 0.155
% C1 r2 ep2: 0.066
% C2 r1 ep2: 0.191
% C2 r2 ep2: 0.094
% C3 r1 ep2: 0.141
% C3 r2 ep2: 0.083
% Improvement in Episode 2: 
% C1 r1: 0.602
% C1 r2: 0.845
% C2 r1: 0.527
% C2 r2: 0.793
% C3 r1: 0.619
% C3 r2: 0.805
% ------------------------------------
\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Quantitative comparison of performances' $L_2$ norm.}
    \centering
    \begin{tabular}{c c c c c c c}
    \hline
		& \multicolumn{3}{c}{\textbf{Episode 1}}  & \multicolumn{3}{c}{\textbf{Episode 2}} \\
    \hline
	\hline 
		& (C$_1$) & (C$_2$) & (C$_3$) & (C$_1$) & (C$_2$) & (C$_3$) \\
	\hline
		$r_1$ & $0.389$ & $0.403$ & $0.370$ & $0.155$ & $0.191$ & $0.141$ \\ 
	\hline
        $r_2$ & $0.426$ & $0.456$ & $0.427$ & $0.066$ & $0.094$ & $0.083$ \\
	\hline
    \end{tabular}
    \label{tab:sim:L2}
\end{table}

>>>>

% ------------------------------------
% Comparative Study
% ------------------------------------
For a comparative study, we implemented 4 controllers.
The properties of the controllers are summarized in Table~\ref{table:controllers}.

@@

% ------------------------------------
% Controllers: CONAC without ctrl cstr
% ------------------------------------
\subsubsection*{Controller 4: (C$_4$) CONAC without control input constraints}

The controller 4 is the same as (C$_1$) but without the control input constraints, to show the effect of the control input constraints.
In this case, the update rate of the Lagrange multipliers regarding the control input constraints \ie $\beta_{\rbu},\beta_{\overline{\tau}_2},\beta_{\underline{\tau}_2}$ was set to $0$, so that $[\lambda_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}$ are not updated.

@@

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers used in simulation}
    \label{table:controller}
    \centering
    \begin{tabular}{c l l}
    \hline
        \!&\!\bf{Description}\!&\!\bf{Input Constraint}\!\\
    \hline
    \hline
        (C$_1$)\!&\!proposed\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau}_2=2.5$ \\
    \hline
        (C$_2$)\!&\!aux. sys.\!&\!$\overline{\tau}_1\!=\!-\underline{\tau}_1\!=\!9.682,\overline{\tau_2}\!=\!-\underline{\tau_2}\!=\!2.5$\!\\
    \hline
        (C$_3$)\!&\!small $\beta_i$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
    \hline
        (C$_4$)\!&\!no $\rbu$ constraints\!&\!$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$ \\
    \hline
    \end{tabular}
    \label{table:controllers}
\end{table}

@@

% ------------------------------------
% Norm of error in Episode 1: 
% C1 r1 ep1: 0.389
% C1 r2 ep1: 0.426
% C2 r1 ep1: 0.403
% C2 r2 ep1: 0.456
% C3 r1 ep1: 0.370
% C3 r2 ep1: 0.427
% Norm of error in Episode 2: 
% C1 r1 ep2: 0.155
% C1 r2 ep2: 0.066
% C2 r1 ep2: 0.191
% C2 r2 ep2: 0.094
% C3 r1 ep2: 0.141
% C3 r2 ep2: 0.083
% Improvement in Episode 2: 
% C1 r1: 0.602
% C1 r2: 0.845
% C2 r1: 0.527
% C2 r2: 0.793
% C3 r1: 0.619
% C3 r2: 0.805
% ------------------------------------
\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Quantitative comparison of performances' $L_2$ norm.}
    \centering
    \begin{tabular}{c c c c c}
    \hline
		& \multicolumn{4}{c}{\textbf{Episode 1}} \\
    \hline
	\hline 
		& (C$_1$) & (C$_2$) & (C$_3$) & (C$_4$) \\
	\hline
		$r_1$ & $0.389$ & $0.403$ & $0.370$ & $0.370$ \\ 
	\hline
        $r_2$ & $0.426$ & $0.456$ & $0.427$ & $0.370$ \\
	\hline
        & \multicolumn{4}{c}{\textbf{Episode 2}} \\
    \hline
    \hline
        & (C$_1$) & (C$_2$) & (C$_3$) & (C$_4$) \\
	\hline
		$r_1$ & $0.389$ & $0.403$ & $0.370$ & $0.370$ \\ 
	\hline
        $r_2$ & $0.426$ & $0.456$ & $0.427$ & $0.370$ \\
    \hline
    \end{tabular}
    \label{tab:sim:L2}
\end{table}
